---
fontsize: 12pt
header-includes:
   - \usepackage{fontspec}
   - \setmainfont{Arial}
   - \usepackage{fancyhdr}
   - \setlength{\headheight}{15pt}
   - \usepackage{pdflscape}
   - \usepackage{booktabs}
   - \usepackage{longtable}
   # - \usepackage{draftwatermark}
geometry: "left=1.5cm,right=1.5cm,bottom=1.5cm"
output:
  pdf_document:
    latex_engine: xelatex
---

\thispagestyle{empty}
\pagestyle{fancy}
\rhead{Introduction to RMarkdown} <!-- Short title of Report -->
\lhead{}
\rfoot{\thepage}
\cfoot{\includegraphics[width = 1cm]{images/hex-rmarkdown}}

\begin{minipage}[]{0.3\textwidth}
\includegraphics[width = 4cm]{images/hex-rmarkdown}
\end{minipage}
\begin{minipage}[]{0.7\textwidth}
%%% <!-- Title of Report-->
\LARGE {Introduction to RMarkdown}\\
%%% <!-- Title of Report Line 2-->
\Large{Laurier Summer Institute of Research Methods}\\
\end{minipage}

\raggedright  <!--removes hyphenation  -->
\vspace{0.5cm}

# Background
This document is intended as an example of using RMarkdown and LaTex to create professional looking reports.   

This R Chunk filters out the school so that all analyses in the document is specfic to that school. 
```{r}

temp <- df %>% 
  dplyr::filter (school == sch)

n_students <- length (temp$RespondentID)

```

In total there were `r n_students` students from `r sch`. 

\newpage

# Results

```{r}
summary_table %>% 
  dplyr::filter(school == sch) %>% 
  ggplot (aes(response, Percent)) + 
  geom_col (fill = "#04559F") + 
  scale_y_continuous(labels = scales::percent_format(accuracy = 1),
                     limits = c(0,1)) + 
  geom_text (aes (label = scales::percent(Percent, accuracy = 1.1)),
             vjust = -1) +
  facet_wrap (~question, scales = "free")
```
